---
title: "Reproducing Code: Report"
author: "Kamila Kolpashnikova"
date: '2022-10-07'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

The project was fully reproducible. All outputs and graphs were possible to replicate. Code was provided, but the program was clear enough to walk through the same steps.

## Replicator's Computing Environment

### Software
- Edition Windows 10 Pro
- Version 10.0.19044
- Installed on 4/11/2020
- R version: 4.2.1 (2022-06-23 ucrt) -- "Funny-Looking Kid"

### Hardware
- Processor Intel(R) Core(TM) i7-10610U CPU @ 1.80GHz   2.30 GHz
- Installed RAM 32.0 GB
- System type 64-bit operating system, x64-based processor

## Replication Steps

1.	Load necessary packages into R (readr, tidyverse, ggplot2) and import ‘gss_12M0025_E_2017_c_31_F1.csv’
2.	Create table of interest from main GSS using variables: 
- decimal age (AGEDC), 
- subjective well-being (SLM_01), 
- self-rated health (SRH_110), 
- self-rated mental health (SRH_115), 
- satisfaction with time spent with children (STS_410), 
- and total personal income (TTLINCG2).

3.	Clean this data
a.	Drop skipped answers (values 96-99) from subjective well-being (SLM_01)
b.	Drop skipped answers (values 6-9) from self-rated health (SRH_110)
c.	Drop skipped answers (values 6-9) from self-rated mental health (SRH_115)
d.	Drop skipped answers (values 6-9) from satisfaction with time spent with children (STS_410)

```{r load-packages, include=FALSE}
library(readr)
library(tidyverse)
library(ggplot2)
library(dplyr)
```

```{r}
gss <- read.csv('data/gss-12M0025-E-2017-c-31_F1.csv') %>%
  select(c(PUMFID, AGEDC, SLM_01, SRH_110, SRH_115, 
           STS_410, TTLINCG2, WGHT_PER)) %>% 
  filter(SLM_01 < 96, SRH_110 < 6, SRH_115 < 6, STS_410 < 6)
```

4.	Create a basic linear regression model estimating subjective well-being using the other 5 variables and note coefficients, significant variables, and R-sq

```{r}
model <- lm(SLM_01 ~ AGEDC + SRH_110 + SRH_115 + STS_410 + TTLINCG2, data = gss)
summary(model)
```

5.	Check assumptions of the model (Independence can be assumed):
a.	Linearity assumption: isolate the first graph of the plot function

```{r, echo=FALSE}
plot(model, which=1)
```

b.	Equal variance assumption: isolate the third graph of the plot function

```{r, echo=FALSE}
plot(model, which=3)
```

c.	Normality assumption:
plot(model, which=2)
```{r, echo=FALSE}
plot(model, which=2)
```

i.	Isolate the second graph of the plot function 
ii.	Create a basic histogram of residuals with 20 bins, pink bars with black outlines, and appropriate title/axis labels

```{r, echo=FALSE}
ggplot(data = gss, aes(x = model$residuals)) +
  geom_histogram(bins = 20, fill = 'pink', color = 'black') +
  labs(title = 'Histogram of Residuals', x = 'Residuals', y = 'Frequency')
```


## Code Testing Summary

|Figure or Table | Relevant program | Replicated (comments) |
|---------------------|----------------------|-----------------------|
|Output 1 | code.R | Yes |
|Figure 1 | code.R | Yes |
|Figure 2 | code.R | Yes |
|Figure 3 | code.R | Yes |
|Figure 4 | code.R | Yes |

## Discrepancies

There were no discrepancies observed.

## Classification

Full reproduction.
